RNA-seq from 4 cell populations

### 2021-07-30 deconvolution/fans4/molec_profiling.Rmd
bug fix

  geneTab = AnnotationDbi::select(ensdb, keys=names(isexpr[isexpr]), columns=c("GENEID", "GENEBIOTYPE"), keytype="GENEID")

@@

    geneTab = AnnotationDbi::select(ensdb, keys=rownames(tab), columns=c("GENEID", "GENEBIOTYPE"), keytype="GENEID")

>>>>

  geneTab = AnnotationDbi::select(EnsDb.Hsapiens.v86, keys=names(isexpr[isexpr]), columns=c("GENEID", "GENEBIOTYPE"), keytype="GENEID")

@@

    geneTab = AnnotationDbi::select(EnsDb.Hsapiens.v86, keys=rownames(tab), columns=c("GENEID", "GENEBIOTYPE"), keytype="GENEID")
